%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[top=0.7in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{setspace}
\usepackage[adobe-utopia]{mathdesign}
\usepackage[T1]{fontenc}

\singlespacing
%\onehalfspacing
%\doublespacing
%\setstretch{1.1}
%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\setlength{\textwidth}{6.0in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\centerline{\huge\bf Ajil Jalal} % Your name at the top
915 E 41 ST, APT 203 \hfill Email: ajiljalal@utexas.edu\\
Austin, TX- 78751\hfill Website: \href{https://sites.google.com/site/ajiljalal}{https://sites.google.com/site/ajiljalal}\\
\vbox{\hrule width\textwidth height 3pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
%\centerline{915 E 41 ST, APT 203} % Your address
%\centerline{Austin, Texas 78751}
%\centerline{Phone: (512) 888-7861 }
%\centerline{Email: ajiljalal@utexas.edu }
%\centerline{Website: \href{https://sites.google.com/site/ajiljalal}{https://sites.google.com/site/ajiljalal}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{\large Education}
{\bf University of Texas at Austin} \hfill 2016-Present\\
{\sl Ph.D., Electrical and Computer Engineering} \hfill GPA: 4.0/4.0 \\
{\sl Advisor}: Prof. Alexandros G. Dimakis \\
{\sl Interests}: Statistical Machine Learning, Information and Coding Theory, Generative Models

{\bf Indian Institute of Technology Madras} \hfill 2012-2016\\
{\sl Bachelor of Technology (Honours) in Electrical Engineering} \hfill GPA: 9.06/10 \\
{\sl Advisors}: Prof. Krishna Jagannathan and Prof. Rahul Vaze \\
{\sl Minor}: Systems Engineering 

\section{\large Publications} 
Ashish Bora, {\bf Ajil Jalal}, Eric Price, Alexandros G. Dimakis, ``Compressed Sensing Using Generative Models", ICML 2017, Sydney, Australia.

Umang Bhaskar, {\bf Ajil Jalal}, Rahul Vaze, ``The Adwords Problem with Strict Capacity Constraints", FSTTCS 2016, Chennai, India.


\section{\large Professional \\ Experience} 
{\bf Tata Institute of Fundamental Research} \hfill Mumbai, India\\
Undergraduate Research Intern\hfill Summer 2015\\
Designed approximation algorithms and showed approximation bounds for an online combinatorial optimization problem.

{\bf Audience Communication Systems} \hfill Bangalore, India\\
Undergraduate Intern \hfill Summer 2014\\
Worked on a text dependent automatic speaker recognition system.

{\bf Audience Communication Systems} \hfill Bangalore, India\\
Undergraduate Intern \hfill Winter 2013\\
Worked on reducing power dissipation in MIPS processors by minimising switching activity
in the processor.

\section{\large Projects}

{\bf Compressed Sensing Using Generative Models}\hfill August 2016- Present\\
{\sl UT Austin, with Prof. Alexandros G. Dimakis and Prof. Eric Price}
\begin{itemize}
	\item Introduced a new approach to compressed sensing. Traditional compressed sensing tries to find a sparse solution to an under-determined system of linear equations.
	\item Our approach is to search for an approximate solution in the span of a generative model.
	\item Proved upper bounds on number of measurements required for recovering a solution with low $\ell_2$ error. Empirical results show that we require $10$x less measurements than the traditional LASSO algorithm.
\end{itemize}

\pagebreak

{\bf The Adwords Problem with Strict Capacity Constraints} \hfill May 2015- May 2016\\
{\sl TIFR, with Prof. Rahul Vaze and Prof. Umang Bhaskar}
\begin{itemize}\itemsep -2pt
	\item An adversary produces weighted jobs to a set of servers with finite capacities at discrete	time steps, and a matching must be found at each time step. Objective is to maximize the aggregate sum of jobs matched.
	\item Designed a randomised online algorithm and proved an approximation factor of 6.
	Designed and proved that a deterministic online algorithm achieves an approximation
	factor of 3 for a restricted case. Also showed that a load balancing algorithm is near-optimal for a special case.
	\item Proved lower bounds which show our algorithms are almost tight.
\end{itemize}

{\bf Text Dependent Automatic Speaker Recognition} \hfill Summer 2014\\
{\sl Audience Communication Systems, with Murali Deshpande and Vinay N Krishnan}
\begin{itemize}\itemsep -2pt
	\item Implemented an adaptive Gaussian Mixture Model which can be trained to recognise a particular
	keyphrase by a 	user. Can be used as part of a voice activated wake up feature for
	cellphones.
	\item Model uses approximately 10 seconds of training data per user and achieves 80\%+ accuracy.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\large Honors}
\begin{itemize}\itemsep -2pt
	\item Ranked {\bf 535} nationally in the {\bf 2012 IITJEE}, among 700,000 competitors.
	\item {\bf Karnataka Regional Mathematical Olympiad} scholar. Attended the {\bf Indian National Mathematical Olympiad (INMO)} camp and represented Karnataka
	in the INMO, 2011.
	\item {\bf Kishore Vaigyanik Protsahan Yojana (KVPY)} fellow, 2012.
	\item Honorable Mention in {\bf Quantify}, an analytics competition organised by Goldman-Sachs,
	2015.
	\item Nominated for the {\bf INSPIRE} scholarship, awarded to the top 1\% in the CBSE grade XII
	examinations, 2012.
	\item Ranked {\bf 63} in the {\bf Kerala Common Entrance Examination(CEE)}, 2012.
\end{itemize}

\section{\large Teaching \\ Experience}
{\bf University of Texas at Austin:}\\
{\sl Teaching Assistant}, EE351K: Introduction to Probability and Statistics \hfill Spring 2017\\
{\sl Teaching Assistant}, EE360C: Algorithms \hfill Fall 2016

\section{\large Skills}
{\sl Programming languages:} Python, C, C++.\\
{\sl Libraries and Toolkits:} Tensorflow, Matlab, \LaTeX, Numpy, Scipy.

\section{\large Relevant \\ Courses}

\setlength\tabcolsep{15pt}
\begin{tabular}{ll}
	Machine Learning & Information Theory \\
	Error Control Coding & Convex Optimization Theory and Algorithms\\
	Probability and Stochastic Processes & Approximation Algorithms \\ 
	Theory of Computation & Adaptive Signal Processing \\
	Digital Communication Systems & Computational Methods in EE \\ 
	Analog and Digital Signal Processing & Modern Control Theory\\
	Network Analysis & Multivariate Data Analysis\\
	Real Analysis & Complex Analysis\\
	Process Optimization & Reinforcement Learning\\
\end{tabular}

\section{Hobbies}
{\sl Music:} Professionally trained in Tabla and completed Preliminary, First Year and Second Year Examinations. All examinations were conducted by the {\bf Bangiya Sangeet Parishad}.\\
{\sl Other:} Soccer, squash, pencil sketching, watercolor and oil painting.

%\section{EXPERIENCE}
%
%{\sl Business Applications Programmer} \hfill Fall 1990 \\
%Allied-Signal Bendix Friction Materials Division, Financial Planning Department, Latham, NY 
%
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Developed four ``user friendly" forecasting systems each of which produces 18 to 139 individual reports. 
%\item Developed or improved almost all IFPS programs used for financial reports. 
%\end{itemize}
% 
%{\sl Research Programmer} \hfill Summer 1990 \\
%Psychology Department, Rensselaer Polytechnic Institute 
%\begin{itemize} 
%\item Performed computer aided statistical analysis of data. 
%\end{itemize} 
%
%{\sl Assistant Manager} \hfill Summers 1988-89 \\
%Thunder Restaurant, Canton, CT
%\begin{itemize}
%\item Recognized need for, developed, and wrote employee training manual. Performed various duties including cooking, employee training, ordering, and inventory control. 
%\end{itemize} 

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

%\section{COMMUNITY \\ SERVICE}
%
%Organized and directed the 1988 and 1989 Grand Marshall Week \\
%``Basketball Marathon.'' A 24 hour charity event to benefit the Troy Boys Club. Over 250 people participated each year. 
%
%%----------------------------------------------------------------------------------------
%%	EXTRA-CURRICULAR ACTIVITIES SECTION
%%----------------------------------------------------------------------------------------
%
%\section{EXTRA-CURRICULAR \\ ACTIVITIES} 
%
%Elected {\it House Manager}, Rho Phi Sorority \\
%Elected {\it Sports Chairman} \\
%Attended Krannet Leadership Conference \\
%Headed delegation to Rho Phi Congress \\
%Junior varsity basketball team \\
%Participant, seven intramural athletic teams 
%
%%----------------------------------------------------------------------------------------

\end{resume}
\end{document}